---
title: "Creative Assignment 1"
author: "Zoe Iacovino"
date: "9/13/2020"
output: html_document
toc_depth: 2
---
# New Orleans

```{r, Loading Library, census, results= 'hide', message=FALSE}
library(tidyverse)
library(tidycensus)
library(ggplot2)
library(prettydoc)
library(ggthemes)
area_vars_2010 <- load_variables(2010, "sf1")
```

##Loading Data

I selected 8 variables: 
<ul>
<li> The total of housing units:H001001
<li> The total of households in urbanized areas: H002003
<li> The total units that are vacant: H005001
<li> The total of vacant units used seasonally: H005006
<li> The total population: P001001
<li> The race of the primary householder: H005008
<li> The percentage of houses with three or more generations:PCT014002
<li> THe Median age of residents P013001
</ul>

From these, I am intersested in 
<ul>
<li> The percentage of units that are vacant
<li> The percentage of the units that vacant seasonally
<li> The percentage of vacant units in urbanized areas
<li> The race of householders
<li> The percentage of multigeneration housholds
<li> Whether a tract is urban or not


```{r Choosing variables, results='hide', message=FALSE}
vars <- c(tot_hh = "H001001",
         tot_urban_hh = "H002003",
         tot_vacant = "H005001",
         tot_vacant_fr = "H005002",
         tot_vacant_rno = "H005003",
         tot_vacant_fs = "H005004",
         tot_vacant_sno = "H005005",
         tot_vacant_seas = "H005006",
         tot_vacant_migr = "H005007",
         tot_pop = "P001001",
         race_hholder = "H006001",
         hh_multigen = "PCT014002",
         med_age = "P013001",
         nh_white_hhr = "H006002",
         nh_black_hhr = "H006003",
         nh_asian_hhr = "H006005",
         hispanic_hhr = "H007010",
         twop_hhr = "H006008")

NOLA_tracts <- get_decennial(geography = "tract", variables = vars,
                           state = "LA", county = "Orleans",
                           output = "wide") %>%
  mutate(urban = (tot_urban_hh == tot_hh) ,
         pct_multigen = (hh_multigen/ tot_hh),
         pct_vacant = (tot_vacant/tot_hh),
         pct_vac_seasonal = (tot_vacant_seas/ tot_vacant*100),
         pct_vac_forrent = (tot_vacant_fr/ tot_vacant),
         pct_vac_rented = (tot_vacant_rno/ tot_vacant),
         pct_vac_forsale = (tot_vacant_fs/ tot_vacant),
         pct_vac_sold = (tot_vacant_sno/ tot_vacant),
         pct_vac_migrant = (tot_vacant_migr/ tot_vacant),
         pct_vac_urb = (tot_vacant / tot_urban_hh),
         maj_rac_eth_hhr = case_when(
           nh_white_hhr / race_hholder > 0.5 ~ "hhr_white",
           nh_black_hhr / race_hholder > 0.5 ~ "hhr_black",
           nh_asian_hhr / race_hholder > 0.5 ~ "hhr_asian",
           hispanic_hhr / race_hholder > 0.5 ~ "hispanic",
           twop_hhr /race_hholder > 0.5 ~ "multiracial",
           (nh_white_hhr + nh_black_hhr + nh_asian_hhr + hispanic_hhr + twop_hhr) /
             race_hholder < 0.5 ~ "other",
           TRUE ~ "None"))%>%
  filter(tot_pop > 0, tot_hh > 0) %>%
  select(GEOID, urban, pct_vacant, pct_vac_urb, tot_vacant_seas, tot_vacant_fr, tot_vacant_rno, tot_vacant_fs, tot_vacant_sno, tot_vacant_migr, pct_vac_seasonal, pct_multigen, maj_rac_eth_hhr, tot_hh, tot_pop, med_age) 
```
<b> Final Variables Chosen </b>
The dataset includes 173 tracts in Orleans Parish with 15 variables, the main of which are: 
<ol>
<li> *urban* The units in urbanized tracts, categorical
<li> *maj_rac_eth_hhr* The majority of householders by race
<li> *pct_vacant* The percentage of units that are vacant, as well as variables that break it down into for rent, rented, for sale, sold, seasonal, and for migrant workers.
<li> *pct_vac_urb* The percentage of vacant units that are in urbanized areas
<li> *pct_multigen* Percentage of houses with three or more generations
</ol>

```{r Plotting 1}
ggplot(NOLA_tracts, 
       aes(x = pct_multigen,
           y = med_age,
           size = tot_hh,
           shape = urban,
           color = urban
           )) +
  geom_point() +
  scale_size_continuous(name = "Households in Tract") +
  scale_x_continuous(name = "Percent of vacant homes",
                     breaks = seq(0, 1, by = 0.1),
                     labels = paste(seq(0, 100, by = 10), "%", sep = "")) +
  scale_y_continuous(name = "Median age within tract",
                     breaks = seq(10, 80, by = 10)) +
  scale_shape(name = element_blank(), 
              labels = c("Rural tract", "Urban tract")
              ) +
  theme_bw() +
  theme(legend.key.size = unit(0.1, "cm"))
```

```{r Plotting 2}
ggplot(NOLA_tracts, 
       aes(x = pct_vacant*100,
           y = tot_hh,
           color = "black")) +
  geom_point(alpha = 0.5, size = 1.5, color = "light blue") +
  stat_smooth(color = "#dfc7f2", linetype = 2, size = 1.5) +
  scale_x_continuous(name = "Percent of vacant units",
                     labels = c("100 or 0", "20%", "40%", "60%", "80%", "100%"),
                     breaks = seq(0, 100, by = 20)) +
  scale_y_continuous(name = "Households in Tract",
                     trans = "log",
                     breaks = c(10, 100, 1000, 10000),
                     labels = c("10", "100", "1,000", "10,000")) +
  coord_polar(theta = "x")
  
```
```{r Plotting 3}
ggplot(NOLA_tracts, 
       aes(x = maj_rac_eth_hhr,
           y = pct_multigen)) +
  geom_point() +
  scale_x_discrete(name = "Majority race/ethnicity",
                       labels = c("Asian",
                                  "Black",
                                  "White",
                                  "No majority")) +
  scale_y_continuous(name = "Percentage of Multigenerational homes within tract",
                     breaks = seq(10, 80, by = 10)) +
  theme_tufte() 
```

```{r Plotting 4}
ggplot(NOLA_tracts, 
       aes(x = maj_rac_eth_hhr,
           y = pct_multigen,
           color = maj_rac_eth_hhr)) +
  geom_point(position = "jitter",
             size = 2.5,
             alpha = 0.5) +
  scale_x_discrete(name = "Majority race/ethnicity",
                       labels = c("Asian",
                                  "Black",
                                  "White",
                                  "No majority")) +
  scale_color_economist()   +
  scale_y_continuous(name = "Percentage of Multigenerational homes within tract",
                     breaks = seq(10, 80, by = 10)) +
  theme_economist(base_size = 10, base_family = "sans",
  horizontal = TRUE, dkpanel = FALSE) +
  theme(legend.position = "none")
```


```{r Plotting 5}
ggplot(NOLA_tracts, 
       aes(x = urban,
           y = med_age,
           color = urban)) +
  geom_boxplot() +
  scale_x_discrete(name = "Urbanized or Rural Tract",
                       labels = c("Rural",
                                  "Urban",
                                  "Other"
                                 )) +
  scale_y_continuous(name = "Median age within tract",
                     breaks = seq(10, 80, by = 10)) +
  theme_bw() +
  theme(legend.position = "none")

```
```{r Plotting 6}

ggplot(NOLA_tracts, 
       aes (x=tot_vacant_seas,
            color = urban
           )) + 
  geom_histogram(binwidth = 5) +
  theme_fivethirtyeight(base_size = 10, base_family = "sans")

```
 
```{r Plotting 7}
pie_chart <- ggplot(NOLA_tracts, 
                    aes(x = 1, 
                        fill =  urban)) +
  geom_bar(position = "fill") +
  coord_polar(theta = "y") +
  scale_y_continuous(name = "Number of tracts") +
  scale_fill_discrete(name = "Urban or Rural Tracts",) +
  theme_void() 

pie_chart

```

```{r Plotting 8}
ggplot(data=NOLA_tracts, aes(x=maj_rac_eth_hhr, y=tot_hh)) +
  geom_bar(stat="identity", color = "light blue", fill = "light blue") +
  scale_x_discrete(name = "Race of Householder", 
                 labels = c("Asian", "Black", "White", "Other"))+
  scale_y_continuous(name= "Total Households")
```

```{r Plotting 9}
ggplot(data=NOLA_tracts, aes
       (x=maj_rac_eth_hhr, y=pct_multigen*100, group = urban), 
        geom_line(linetype= dashed)+
       scale_y_continuous(name = "Percent Multigenerational Households", 
                          breaks = seq(0, 5, by = 1))
  
)
```
ok so apparently i can't draw a line??? cute

#Taelor
Haha, happens to the best of us.

Your missing a ) and a + at the end of your first line of code 
ggplot(data=NOLA_tracts, aes(x=maj_rac_eth_hhr, y=pct_multigen*100, group = urban)) +

You'll need "" around dashed for R to recognize the command 
geom_line(linetype= dashed)

And you can delete that last parentheses. 

After I made those changes R graphed your data! But I left your original code untouched in case you wanted to do or add anything else to it. 




```{r Plotting 10}
ggplot(NOLA_tracts, aes(x = maj_rac_eth_hhr, fill = urban)) +
  geom_bar(position = "fill") +
  scale_y_continuous(name = "percent of tracts",
                     breaks = seq(0, 1, by = 0.1),
                     labels = paste(seq(0,100, by = 10), "%", sep ="")) +
  scale_x_discrete(name = "Majority race/ethnicity",
                       labels = c("Asian",
                                  "Black",
                                  "White",
                                  "No majority")) +
  scale_fill_discrete(name = element_blank(),
                        labels = c("Rural tracts",
                                   "Urban tracts")) +
  theme_minimal()
```

