---
title: "Creative Assignment 3"
author: "Zoe Iacovino"
date: "9/27/2020"
output: html_document
---
```{r Libraries, results = 'hide', message = FALSE}
library(sf)
library(tidyverse)
library(ggthemes)
library(ggspatial)
library(units)
library(nngeo)
```
Because I have already been working Boston data for studio, I am going with Boston data for this assignment. 

Points A: Vision Zero Crash Records

Points B: Locations of Pedestrian Ramps

Polygons C: Boston Zip Codes

Polygons D: Boston Open Spaces


## Loading Datasets

```{r Datasets}
MA_state_plane <- "+proj=lcc +lat_1=41.71666666666667 +lat_2=42.68333333333333 +lat_0=41 +lon_0=-71.5 +x_0=200000 +y_0=750000 +ellps=GRS80 +units=m +no_defs"

lat_lon_CRS <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"



#Points A: Accidents 
accidents <- st_as_sf(read.csv("Vision_Zero_Crash_Records.csv"), 
                      coords = c("long", "lat"), 
                      crs= lat_lon_CRS)


#Points B: Pedestrian Ramps 
ramps <- st_read("https://opendata.arcgis.com/datasets/ee5ae0ec9a3e4ba9b12a3f16415cc370_3.geojson",
                quiet = TRUE)

#Polygon C: Zip Codes
zipcodes<- st_read("https://opendata.arcgis.com/datasets/53ea466a189b4f43b3dfb7b38fa7f3b6_1.geojson",
                quiet = TRUE)

#Polygon D: Open Spaces and Parks 
parks<- st_read("https://opendata.arcgis.com/datasets/2868d370c55d4d458d4ae2224ef8cddd_7.geojson",
                quiet = TRUE)

#Transforming Data

accidents <- accidents %>%
 st_transform(MA_state_plane)

ramps <- ramps %>%
  st_transform(MA_state_plane)

zipcodes <- zipcodes %>%
  st_transform(MA_state_plane)

parks <- parks %>%
  st_transform(MA_state_plane)



ggplot() +
  geom_sf(data = zipcodes, fill = NA, color = "black", size = 2)+ 
  geom_sf(data = parks, fill = "darkgreen")+ 
  geom_sf(data = ramps, size = 0.01) +
  geom_sf(data= accidents, color = "maroon", size = .01) +
  theme_map() +
  annotation_scale()

```


## Spatial Calculations 1
The number and proportion of accidents [points] within a specified distance of pedestrian ramp [points]

```{r Spatial Calculations 1}

ramps_buffer <- st_buffer(ramps, dist = 10)%>%
  st_union()

ggplot(ramps_buffer)+
  geom_sf()+
  theme_map()

accidents_ramps <- accidents[ramps_buffer,]

ggplot(ramps_buffer) +
  geom_sf() +
  geom_sf(data = accidents_ramps, 
          color = "red", 
          size = 0.01) +
  theme_map()


accidents <- accidents %>%
  st_join(accidents_ramps)%>% 
  mutate(by_ramps = !is.na(dispatch_ts.y))

n_ramps_accidents <- sum(accidents$by_ramps)

n_ramps_accidents

n_accidents <- length(accidents$by_ramps)

pct_ramps_accidents <- n_ramps_accidents/ n_accidents

pct_ramps_accidents


#Plotting the Percentage of Accidents 10 Meters from a Pedestrian Ramp

left_side  <- st_bbox(accidents)$xmin
top_side <- st_bbox(accidents)$ymax

ggplot() +
  geom_sf(data = accidents, size = 0.01,
          aes(color = by_ramps)) +
  scale_color_manual(values = c("#8C7268", "#591931"),
          name = "Car, Bike, and Pedestrian Accidents\nby distance to a Pedestrian Ramp", 
          labels = c("No accident within 10 m",
                     "Accident within 10 m")) +
  annotation_scale(location = "br") +
  annotation_north_arrow(location = "tr",
                         style = north_arrow_minimal()) +
  annotate(geom = "text", x = left_side, 
           y = top_side, 
           label = paste("Of the ", 
                         prettyNum(n_accidents, big.mark = ","),
                         " accidents in Boston\n", 
                         prettyNum(n_ramps_accidents, big.mark = ","),
                         " (", 
                         prettyNum(100*pct_ramps_accidents, digits = 0),
                         "%) are within 10\nmeters of a pedestrian ramp.",
                         sep = ""),
           hjust = 0, vjust = 1, size = 3) +
  theme_map() +
  theme(panel.background = element_rect(fill = "#4D5059"),
        legend.background = element_rect(fill = alpha("white", 0.5), 
                                         color = "gray"))

```


## Calculations 2
The average density of accidents [points] in each zipcode [polygon].
```{r Calculations 2}

zipcodes <- zipcodes %>%
  mutate(area = set_units(st_area(zipcodes), km^2)) %>%
  mutate(num_accidents = lengths(st_covers(zipcodes, accidents)))%>%
  mutate(accidents_dens = as.numeric(num_accidents/area))

ggplot(zipcodes) +
  geom_sf(color = NA, 
          aes(fill = accidents_dens)) +
    scale_fill_viridis_c(name = 
                           "Boston Zipcodes\nby density of car, bike\nand pedestrian accidents",
                         ) +
  annotation_scale(location = "br") +
  annotation_north_arrow(location = "tr",
                         style = north_arrow_minimal()) +
theme_map() +
  theme(legend.position = "right",
    legend.background = element_rect(fill = alpha("white", 0.5), 
                                         color = "gray"))
```


## Calculations 3
The average density of ramps [points] in each zipcode [polygon].

```{r Spatial Calculations 3}
#The number of Ramps in each Zipcodes
zipcodes <- zipcodes %>%
  mutate(num_ramps = lengths(st_covers(zipcodes, ramps)))

ggplot(zipcodes)+
  geom_sf(color = NA,
          aes(fill = num_ramps))+
  scale_fill_viridis_b(name = "Boston Zip Codes\nby number of\nPedestrian Crossing Ramps")+
  annotation_scale(location = "br")+
  annotation_north_arrow(location = "tr",
                         style = north_arrow_minimal())+
  theme_map()+
   theme(legend.background = element_rect(fill = alpha("white", 0.5),
                                          color = "gray"))


#Calculations 3.5 

zipcodes <- zipcodes %>%
  mutate(area = set_units(st_area(zipcodes), km^2))%>%
  mutate(ramps_dens = as.numeric(num_ramps / area))

ggplot(zipcodes)+
  geom_sf(color = NA,
          aes(fill = ramps_dens))+
  scale_fill_viridis_b(name = "Boston Zip Codes\nby density of\nPedestrian Crossing Ramps\nper square km"
                    )+
  annotation_scale(location = "br")+
  annotation_north_arrow(location = "tr",
                         style = north_arrow_minimal())+
  theme_map()+
   theme(legend.background = element_rect(fill = alpha("white", 0.5),
                                          color = "gray"))

  

```


## Calculations 4
The number and proportion of zip codes [polygons] that overlap with open space [polygons].
```{r Calculations 4}
zipcodes <- zipcodes %>%
  mutate(num_parks = lengths(st_overlaps(zipcodes, parks))) %>%
  mutate(has_parks = num_parks > 0)

n_parks_zips <- sum(zipcodes$has_parks)

n_parks_zips

left_side  <- st_bbox(parks)$xmin
top_side <- st_bbox(parks)$ymax

ggplot(parks) +
  geom_sf(fill = "lightgray", color = NA) +
  geom_sf(data = zipcodes,
          aes(fill = has_parks)) +
  scale_fill_manual(values = c("#4D5059", "#707358"),
          name = "Boston Zipcodes\nby presence of a park or open space", 
          labels = c("Zipcode without\nan open space or park",
                     "Zipcode with an\nopen space or park")) +
  annotation_scale(location = "br") +
  annotation_north_arrow(location = "tr",
                         style = north_arrow_minimal()) +
  annotate(geom = "text", x = left_side, 
           y = top_side - 1000, 
           label = paste(n_parks_zips ,
                         "of Boston's", 
                         length(zipcodes$ZIP5),
                         "zipcodes contain\nor overlap with", 
                         "a park or open space."),
           hjust = 0, vjust = 0, size = 3) +
  theme_map() +
  theme(panel.background = element_rect(fill = "gray"),
        legend.background = element_rect(fill = alpha("white", 0.5), 
                                         color = "gray"))


```


## Calculations 5
The number and proportion of open space [polygons] containing accidents [points].
```{r Calculations 5}

#number of parks with accidents
parks <- parks %>%
  mutate(num_accidents = lengths(st_covers(parks, accidents)))

accidents <- accidents %>%
  st_join(parks)%>%
  mutate(in_parks = !is.na(dispatch_ts.y))

n_park_crash <- sum(accidents$in_parks)

n_accidents <- length(accidents$in_parks)

pct_parks_accidents <- n_park_crash / n_accidents

pct_parks_accidents

ggplot(parks)+
  geom_sf(color = NA, aes(fill = num_accidents))+
  scale_fill_viridis_c(name = "Boston parks containing a car,\nbike, or pedestrian accident")+
  annotation_scale(location = "br") +
  annotation_north_arrow(location = "tr",
                         style = north_arrow_minimal(fill= "white")) +
  theme_map() +
  theme(panel.background = element_rect(fill = "#262226"),
        legend.background = element_rect(fill = alpha("white", 0.5), 
                                         color = "gray"))

#annotate(geom = "text", x = left_side, 
           #y = top_side - 1000),
           #hjust = 0, vjust = 0, size = 3) +

```


The average (Euclidean) distance between accidents [points] and their nearest respective ramps [points].
```{r Calculation 6}
accidents <- accidents %>%
  mutate(ramps_dist = st_nn(accidents,ramps, 
                           returnDist = TRUE)$dist) %>%
  mutate(ramps_dist = as.numeric(ramps_dist))


avg_ramps_dist <- mean(accidents$ramps_dist)

avg_ramps_dist


```

```{r}
parks <- parks %>%
  mutate(area = set_units(st_area(parks),ft^2))

parks_CT <-parks %>%
  filter(DISTRICT=="Charlestown")

park_per_bos <- sum(as.numeric(parks$area))/694583

park_per_CT <- sum(as.numeric(parks_CT$area))/19414

```

