---
title: "Creative Assignment 2"
author: "Zoe Iacovino"
date: "9/20/2020"
output: html_document
 
---
```{r Loading Librarys, results='hide', message=FALSE}

                 
library(ggplot2)
theme_set(theme_bw())
library(sf)
library(sp)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(rgeos)
library(ggspatial)
library(tidyverse)
library(cartogram)
library(ggthemes)
library(wesanderson)
library(prettydoc)

pal <- wes_palette("Zissou1", 100, type = "continuous")

world <- ne_countries(scale = 50, returnclass = "sf")

```
# South America: Plotting a Map

First, I plotted South America with the default projection from rnaturalearth on latitude and longitude. 
```{r South America no projection, GDP data}
sa_countries <- world %>%
  filter(continent == "South America")

sa_map <- ggplot(sa_countries) +
  geom_sf(color = "#3d9bb2") + 
  scale_fill_gradientn(colors = pal, name = "GDP")
  

sa_map
```

Next, I used spatial reference to find appopriate projections for South America. I used an Albers Equal Area Projection based on Brazil, a polyconic projection based on Brazil, and a Universal Transverse Mercator Projection based on Chile. 

### AEA Brazil
```{r AEA Projection, SR-ORG:6820 AEA Brazil}
aea_brazil <-"+proj=aea +lat_1=-2 +lat_2=-22 +lat_0=-12 +lon_0=-54 +x_0=0 +y_0=0 +a=6378160 +b=6356537.557298475 +units=m +no_defs"

sa_map_aea <- ggplot(sa_countries) +
  geom_sf(color = "#3d9bb2") +
  coord_sf(crs = aea_brazil)
  

sa_map_aea

```


### Polyconic Brazil
```{r SR-ORG 86 SAD69 Brazil Polyconic Zeroed False Northing and Easting}
polyconic <- "+proj=poly +lat_0=0 +lon_0=-54 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs " 
sa_map_ply <- ggplot(sa_countries) +
  geom_sf(color = "#3d9bb2") +
  coord_sf(crs = polyconic)

sa_map_ply
```


### UTM Chile
```{r SR-ORG:7179 PSAD_1956_UTM_ZONE_19S}
utm_chile <- "+proj=utm +zone=19 +south +ellps=intl +units=m +no_defs "

sa_map_utm <- ggplot(sa_countries) +
  geom_sf(color = "#3d9bb2") +
  coord_sf(crs = utm_chile)

sa_map_utm

```


## Showing the Distribution of A Variable


I used the data already available in rnaturalearthdata, GDP and Population estimates, to make cartograms. My projections all used Brazil AEA. 


```{r Data Preparation, results='hide', message=FALSE}
#Transforming Data

sa_transformed <- sa_countries %>% 
  st_transform(crs = aea_brazil)%>%
  select (name, pop_est, gdp_md_est)
  

#Cartogram
sa_gdp_cartogram <- sa_transformed %>%
  cartogram_cont("pop_est")

sa_gdp_NCcartogram <- sa_transformed %>%
  cartogram_ncont("pop_est")

sa_cartogram_dorling <- sa_transformed %>%
  cartogram_dorling("pop_est")

```


### Continuous Cartogram


The resulting graph is not overly dramatic, but you can see some of the countries almost disappear.
```{r Cartogram 1 Continuous Population}
ggplot(data = sa_gdp_cartogram, aes(fill = gdp_md_est))+
       geom_sf(color = NA) +
  scale_fill_gradientn(
    name = "GDP", colors = pal) +
  theme_map() +
  theme(legend.background = element_blank())

```
### Non-Continuous Cartogram


The separation of the smaller countries is a lot more obvious on this chart. Being able to still see most of the countries also makes it apparent how Brazil is not only the largest country in GDP, but the lack of distortion reflects its higher population.
```{r Cartogram 2 Non Continuous Population}

ggplot(sa_gdp_NCcartogram, aes(fill = gdp_md_est))+
       geom_sf()+
      scale_fill_gradientn(
    name = "GDP", colors = pal) +
      theme_map()+
  theme(legend.background = element_blank())

```

### Dorling Cartogram


Very abstract and stylistic, I thought it would look nice without a legend, and could be used as a cover graphic. 
```{r}

ggplot(sa_cartogram_dorling, aes(fill = gdp_md_est)) +
  geom_sf(color = NA) +
  scale_fill_gradientn( colors= pal,
    name = "GDP") +
  theme_map() +
  theme(legend.position = "none")
  
```


